Ab Initio Effective One-Electron Potential Operators: Applications for Charge-Transfer Energy in Effective Fragment Potentials

### 2019-11-13 papers/2_oep_technique/paper-r2.tex
Figure 2 added to the manuscript. Computational details elaborated.

\paragraph{Group (iii).}
The terms with the overlap integrals involving the occupied MO on $A$
can be combined into a single summation term, i.e.,
\begin{multline}
       - \sum_{j\in B}^{\rm Occ} S_{ij} \tBraKet{j}{\hat{v}^A_{i} }{n}  
     + \sum_{k\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}  
        S_{kj} \left( 1 - \delta_{ik} \right)
        \BraKet{nj}{ik} \\ = -
 \sum_{k\in A}^{\rm Occ} 
 \sum_{j\in B}^{\rm Occ}
 S_{kj} 
 \tBraKet{j}{
 \underbrace{
 \left\{ 
  \delta_{ik} \left( \hat{v}^A_{k} + \hat{v}^A_{ik} \right)   - \hat{v}^A_{ik}
 \right\} 
  }_{\hat{v}^{A,{\rm eff}}_{ik}}
 }{n}  \\ \cong -
%
  \sum_{k\in A}^{\rm Occ} 
 \sum_{j\in B}^{\rm Occ}
 S_{kj} 
 \rho_{nj}^B \odot \rho^{A,{\rm eff}}_{ik} \;,
\end{multline}
%
where the effective potential ${v}^{A,{\rm eff}}_{ik}$ (with the associated 
effective density $\rho^{A,{\rm eff}}_{ik}$) 
is defined by
%
\begin{equation} \label{e:ct.group-iii.oep}
 {v}^{A,{\rm eff}}_{ik}({\bf r}) \equiv
 \delta_{ik} 
 \left[
  v^A_{\rm tot} ({\bf r}) - 2 v^A_{kk} ({\bf r}) + v^A_{ik} ({\bf r})
 \right] 
  - v^A_{ik} ({\bf r}) \;.
\end{equation}
%
Now, it is first assumed here that $\rho^{B}_{nj} ({\bf r}) \approx 0$ if occupied MO's on $B$ are localized.
This means that
%
\begin{multline} \label{e:ct.group-iii.final.a}
        - \sum_{j\in B}^{\rm Occ} S_{ij} \tBraKet{j}{\hat{v}^A_{\rm tot} }{n}  
     + \sum_{k\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}  
        S_{kj} \left( 1 - \delta_{ik} \right)
        \BraKet{nj}{ik} \\ 
    \approx 0 \;.
\end{multline}
%
The above result is a crude approximation, since the channels $j\rightarrow n$
are quite important contributions in most of perturbation theory treatments.
%virtual MO's can penetrate the occupied MO's to some extent.
In order to include the $\rho^{B}_{nj}$ density, it is approximately represented here by a set of effective 
cumulative
atomic charges $\{ q^{B,(nj)}_{y} \}$ associated with the effective one\hyp{}particle density matrix
%
\begin{equation}
 D^{B,(nj)}_{\beta\delta} = C_{\beta n} C_{\delta j} \;.
\end{equation}
%
In this work, the effective charges were computed via the CAMM or ESP methods as
discussed in Section~XXX. 
Note now that both effective densities in 
$\rho^B_{jn} \odot \rho^{A,{\rm eff}}_{ik}$ are generally complex and one cannot apply the SOA
for $\rho^{A,{\rm eff}}_{ik}$. In the LMO picture however, it can be shown that
$\rho_{ik} ({\bf r}) \ll \rho_{ii} ({\bf r})$ 
for $i\ne k$ in most locations. Therefore,
the SOA is still applicable in the LMO picture
and the effective potential from Eq.~\eqref{e:ct.group-iii.oep} 
simplifies to
%
\begin{equation} \label{e:ct.group-iii.oep.simplified}
 {v}^{A,{\rm eff}}_{ik}({\bf r}) \approx
 \delta_{ik} \left\{
 {v}^A_{\rm tot} ({\bf r})- 2{v}^A_{kk} ({\bf r}) \right\} \;,
\end{equation}
%
which
leads to 
%
\begin{multline} \label{e:ct.group-iii.final.b}
        - \sum_{j\in B}^{\rm Occ} S_{ij} \tBraKet{j}{\hat{v}^A_{\rm tot} }{n}  
     + \sum_{k\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}  
        S_{kj}
        \BraKet{nj}{ik}  \\
 \approx  -
 \sum_{j\in B}^{\rm Occ} S_{ij}
 \sum_{y\in B}^{\rm At} 
 q^{B,(nj)}_{y} 
 \left[ 
   \sum_{x\in A}^{\rm At}
   \frac{Z_x}{r_{xy}}
  + \frac{2}{r_{iy}}
  - \sum_{k\in A}^{\rm Occ}
    \frac{2}{r_{ky}} 
 \right]
 \;.
\end{multline}
%

\paragraph{Final OEP-based forms of the coupling constant.}
Gathering the results from Eqs. the coupling constant
can be given as follows
%
\begin{subequations}
\begin{align} \label{e:ct-murell-etal.vin.oep}
\Approx{ V_{in}^{A\rightarrow B} }{1}
       &= \sum_{\eta\in B}^{\rm RI} V^B_{n\eta} S_{\eta i} 
 +
S_{ni} u_i^{BA} \;, \\
%
\Approx{ V_{in}^{A\rightarrow B} }{2} &=
\Approx{ V_{in}^{A\rightarrow B} }{1} -
  \sum_{j   \in B}^{\rm Occ} S_{ij}
  \sum_{y   \in B}^{\rm At} q_y^{B,(nj)} w_{yi}^{BA}
\;,
\end{align}
\end{subequations}
%
where the auxiliary variables are
%
\begin{subequations}
\begin{align} \label{e:ct-murell-etal.vin.oep.aux-var}
 u_i^{BA} &\equiv    
 \sum_{y\in B}^{\rm At}
  \frac{Z_y}{ r_{yi} } 
 -
 \sum_{j\in B}^{\rm LC}
  \frac{2}{r_{ji}} 
                \;, \\
 w_{yi}^{BA} &\equiv 
   \sum_{x\in A}^{\rm At}
   \frac{Z_x}{r_{xy}}
  + \frac{2}{r_{iy}}
  - \sum_{k\in A}^{\rm Occ}
    \frac{2}{r_{ky}} 
                \;.
\end{align}
\end{subequations}
%
To compute the interaction energy due to CT from $A$ to $B$ by using the above SOA\hyp{}based
approximations, coupling elements need to be transformed from localized to canonical MO basis, i.e.,
%
\begin{equation} \label{e:ect-oep.prefinal}
 E^{A\rightarrow B} \approx
 2 
 \sum_{i\in A}^{\rm CMO}
 \sum_{n\in B}^{\rm Vir}
 \frac{
 \lvert
   \sum_{i'\in A}^{\rm LMO} L_{ii'}^A
   \Approx{V_{i'n}^{A\rightarrow B}}{} 
 \rvert^2 }{\varepsilon_i - \varepsilon_n} \;,
\end{equation}
%
where ${\bf L}^A$ is the CMO\hyp{}LMO transformation matrix for occupied orbitals of $A$. 
Note however, that the effective potential parameters from the density fitted term of group (i) 
do not involve any occupied orbitals.
Therefore, to save computational costs, only groups (ii) and (iii) need to be transformed
whereas for group (i) the overlap integrals from Eq.~\eqref{e:ct.group-i.final} 
can be already evaluated in CMO basis.
Thus, the final working formula for the interaction energy due to CT from $A$ to $B$ reads
%
\begin{multline} \label{e:ect-oep.final}
 E^{A\rightarrow B} \approx
 2 
 \sum_{i\in A}^{\rm CMO}
 \sum_{n\in B}^{\rm Vir}
 \frac{1}{\varepsilon_i - \varepsilon_n} \times 
 \Bigg(
   \Approx{V_{in}^{A\rightarrow B}}{\rm G1} \\
  +
   \sum_{i'\in A}^{\rm LMO} L_{ii'}^A
   \left\{
   \Approx{V_{i'n}^{A\rightarrow B}}{\rm G2} 
  +\Approx{V_{i'n}^{A\rightarrow B}}{\rm G3}
  \right\}
 \Bigg)^2 \;,
\end{multline}
%
where the subscripts G$n$ ($n$ = 1, 2, 3) denote a particular group of 
terms from Eqs.~\eqref{e:ct.group-i.final}, \eqref{e:ct.group-ii.final} and \eqref{e:ct.group-iii.final.a}
or \eqref{e:ct.group-iii.final.b}. 
The total CT energy is given by the sum of the above contribution and the twin contribution
due to CT from molecule $B$ to $A$.

@@

@@

%
\begin{figure}[t]
\includegraphics[width=0.5\textwidth]{fig-2.eps}
\caption{\label{f:fig-1} {\bf Accuracy of the OEP approach to estimate the charge transfer energy
in the PT/HF formulation.} 
Asymptotic dependencies of the charge transfer energy is plotted for 
(a) water dimer, 
(b) water\hyp{}ammonium complex, and 
(c) ammonium\hyp{}nitrate complex,
where one molecule has been translated by $R$ from the starting geometry
along the vector specified in Fig. 1.
The counterpoise\hyp{}corrected total interaction energy
is also shown for comparison in light grey color in this figure.
All data were obtained at HF/6-31+G** level of theory.
} 
\end{figure}
%

@@

Until this moment in this work, two models have been tested with application of the OEP technique.
In this section, computational cost is estimated from the formulas.
In
Table~\ref{t:oep-costs} 
%
{
\renewcommand{\arraystretch}{1.4}
\begin{table}[b]
\caption[Computational cost of the benchmark and OEP-based methods: calculation of coupling constant]
{{\bf Computational cost of the benchmark and OEP-based methods\footnotemark[1]}
}
\label{t:oep-costs}
\begin{ruledtabular}
\begin{tabular}{lcccccc}
Method             && Murrell et al. &&    EFP2        &&      OEP     \\ 
	\cline{1-7}
Group (i)         &&  &&        &&   $obQ$     \\
Group (ii)        &&  &&        &&   $ob$      \\
Group (iii)       &&  &&        &&   $ob(n+o)$     \\
Total Cost        &&  && $10ob^2 + 2b^3 + o^2b^2$       &&   $ob(Q+n+o)$     \\
\end{tabular}
\end{ruledtabular}
%
\footnotetext[1]{Numbers of: $o$ - occupied molecular orbitals; $b$ - atomic basis functions; $n$ - atoms; 
$Q$ - auxiliary basis functions. It was assumed that the number of virtual orbitals is equal to $b$.}
%
\end{table}
}
%
It is clear that the cost of the OEP\hyp{}based equations is much lesser than the cost of EFP2 method,
and many orders of magnitude lesser than the original theory of Murrell et al.

>>>>

\paragraph{Group (iii).}
The terms with the overlap integrals involving the occupied MO on $A$
can be combined into a single summation term, i.e.,
\begin{multline}
       - \sum_{j\in B}^{\rm Occ} S_{ij} \tBraKet{j}{\hat{v}^A_{i} }{n}  
     + \sum_{k\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}  
        S_{kj} \left( 1 - \delta_{ik} \right)
        \BraKet{nj}{ik} \\ = -
 \sum_{k\in A}^{\rm Occ} 
 \sum_{j\in B}^{\rm Occ}
 S_{kj} 
 \tBraKet{j}{
 \underbrace{
 \left\{ 
  \delta_{ik} \left( \hat{v}^A_{k} + \hat{v}^A_{ik} \right)   - \hat{v}^A_{ik}
 \right\} 
  }_{\hat{v}^{A,{\rm eff}}_{ik}}
 }{n}  \\ \cong -
%
  \sum_{k\in A}^{\rm Occ} 
 \sum_{j\in B}^{\rm Occ}
 S_{kj} 
 \rho_{nj}^B \odot \rho^{A,{\rm eff}}_{ik} \;,
\end{multline}
%
where the effective potential ${v}^{A,{\rm eff}}_{ik}$ (with the associated 
effective density $\rho^{A,{\rm eff}}_{ik}$) 
is defined by
%
\begin{equation} \label{e:ct.group-iii.oep}
 {v}^{A,{\rm eff}}_{ik}({\bf r}) \equiv
 \delta_{ik} 
 \left[
  v^A_{\rm tot} ({\bf r}) - 2 v^A_{kk} ({\bf r}) + v^A_{ik} ({\bf r})
 \right] 
  - v^A_{ik} ({\bf r}) \;.
\end{equation}
%
Now, it is first assumed here that $\rho^{B}_{nj} ({\bf r}) \approx 0$ if occupied MO's on $B$ are localized.
This means that
%
\begin{multline} \label{e:ct.group-iii.final.a}
        - \sum_{j\in B}^{\rm Occ} S_{ij} \tBraKet{j}{\hat{v}^A_{\rm tot} }{n}  
     + \sum_{k\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}  
        S_{kj} \left( 1 - \delta_{ik} \right)
        \BraKet{nj}{ik} \\ 
    \approx 0 \;.
\end{multline}
%
The above result is a crude approximation, since the channels $j\rightarrow n$
are quite important contributions in most of perturbation theory treatments.
%virtual MO's can penetrate the occupied MO's to some extent.
In order to include the $\rho^{B}_{nj}$ density, it is approximately represented here by a set of effective 
cumulative
atomic charges $\{ q^{B,(nj)}_{y} \}$ associated with the effective one\hyp{}particle density matrix
%
\begin{equation}
 D^{B,(nj)}_{\beta\delta} = C_{\beta n} C_{\delta j} \;.
\end{equation}
%
In this work, the effective charges were computed via the Mulliken method as
discussed in Section~XXX. 
Note now that both effective densities in 
$\rho^B_{jn} \odot \rho^{A,{\rm eff}}_{ik}$ are generally complex and one cannot apply the SOA
for $\rho^{A,{\rm eff}}_{ik}$. In the LMO picture however, it can be shown that
$\rho_{ik} ({\bf r}) \ll \rho_{ii} ({\bf r})$ 
for $i\ne k$ in most locations. Therefore,
the SOA is still applicable in the LMO picture
and the effective potential from Eq.~\eqref{e:ct.group-iii.oep} 
simplifies to
%
\begin{equation} \label{e:ct.group-iii.oep.simplified}
 {v}^{A,{\rm eff}}_{ik}({\bf r}) \approx
 \delta_{ik} \left\{
 {v}^A_{\rm tot} ({\bf r})- 2{v}^A_{kk} ({\bf r}) \right\} \;,
\end{equation}
%
which
leads to 
%
\begin{multline} \label{e:ct.group-iii.final.b}
        - \sum_{j\in B}^{\rm Occ} S_{ij} \tBraKet{j}{\hat{v}^A_{\rm tot} }{n}  
     + \sum_{k\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}  
        S_{kj}
        \BraKet{nj}{ik}  \\
 \approx  -
 \sum_{j\in B}^{\rm Occ} S_{ij}
 \sum_{y\in B}^{\rm At} 
 q^{B,(nj)}_{y} 
 \left[ 
   \sum_{x\in A}^{\rm At}
   \frac{Z_x}{r_{xy}}
  + \frac{2}{r_{iy}}
  - \sum_{k\in A}^{\rm Occ}
    \frac{2}{r_{ky}} 
 \right]
 \;.
\end{multline}
%

\paragraph{Final OEP-based forms of the coupling constant.}
Gathering the results from Eqs. the coupling constant
can be given as follows
%
\begin{equation} \label{e:ct-murell-etal.vin.oep}
V_{in}^{A\rightarrow B} 
       \approx 
 G_{1;in}^{A\rightarrow B} 
+G_{2;in}^{A\rightarrow B} 
+G_{3;in}^{A\rightarrow B} \;,
\end{equation}
%
where
%
\begin{subequations}
\begin{align}
 G_{1;in}^{A\rightarrow B} &\equiv \sum_{\eta\in B}^{\rm RI} V^B_{n\eta} S_{\eta i} \;, \\
 G_{2;in}^{A\rightarrow B} &\equiv S_{ni} u_i^{BA} \;, \\
 G_{3;in}^{A\rightarrow B} &\equiv
 -\sum_{j   \in B}^{\rm Occ} S_{ij}
  \sum_{y   \in B}^{\rm At} q_y^{B,(nj)} w_{yi}^{BA}
\;.
\end{align}
\end{subequations}
%
In the above, the auxiliary variables are
%
\begin{subequations}
\begin{align} \label{e:ct-murell-etal.vin.oep.aux-var}
 u_i^{BA} &\equiv    
 \sum_{y\in B}^{\rm At}
  \frac{Z_y}{ r_{yi} } 
 -
 \sum_{j\in B}^{\rm LC}
  \frac{2}{r_{ji}} 
                \;, \\
 w_{yi}^{BA} &\equiv 
   \sum_{x\in A}^{\rm At}
   \frac{Z_x}{r_{xy}}
  + \frac{2}{r_{iy}}
  - \sum_{k\in A}^{\rm Occ}
    \frac{2}{r_{ky}} 
                \;.
\end{align}
\end{subequations}
%
To compute the interaction energy due to CT from $A$ to $B$ by using the above SOA\hyp{}based
approximations, coupling elements need to be transformed from localized to canonical MO basis, i.e.,
%
\begin{equation} \label{e:ect-oep.prefinal}
 E^{A\rightarrow B} \approx 
 2 
 \sum_{i\in A}^{\rm CMO}
 \sum_{n\in B}^{\rm Vir}
 \frac{
 \lvert
   \sum_{i'\in A}^{\rm LMO} L_{ii'}^A
   V_{i'n}^{A\rightarrow B}
 \rvert^2 }{\varepsilon_i - \varepsilon_n} \;,
\end{equation}
%
where ${\bf L}^A$ is the CMO\hyp{}LMO transformation matrix for occupied orbitals of $A$. 
Note however, that the effective potential parameters from the density fitted term of group (i) 
do not involve any occupied orbitals.
Therefore, to save computational costs, only groups (ii) and (iii) need to be transformed
whereas for group (i) the overlap integrals from Eq.~\eqref{e:ct.group-i.final} 
can be already evaluated in CMO basis.
Thus, the final working formula for the interaction energy due to CT from $A$ to $B$ reads
%
\begin{multline} \label{e:ect-oep.final}
 E^{A\rightarrow B} \approx
 2 
 \sum_{i\in A}^{\rm CMO}
 \sum_{n\in B}^{\rm Vir}
 \frac{1}{\varepsilon_i - \varepsilon_n} \times 
 \Bigg(
   G_{1,in}^{A\rightarrow B} \\
  +
   \sum_{i'\in A}^{\rm LMO} L_{ii'}^A
   \left\{
   G_{2,i'n}^{A\rightarrow B}
  +G_{3,i'n}^{A\rightarrow B}
  \right\}
 \Bigg)^2 \;,
\end{multline}
%
where the subscripts $G_n$ ($n$ = 1, 2, 3) denote a particular group of 
terms from Eqs.~\eqref{e:ct.group-i.final}, \eqref{e:ct.group-ii.final} and \eqref{e:ct.group-iii.final.a}
or \eqref{e:ct.group-iii.final.b}. 
The total CT energy is given by the sum of the above contribution and the twin contribution
due to CT from molecule $B$ to $A$,
%
\begin{equation}
 \Delta E^{\rm CT} = E^{A\rightarrow B} + E^{B\rightarrow A} \;.
\end{equation}
%

@@

Four selected molecular pairs composed of H$_2$O, CH$_3$OH, NH$_4^+$ and NO$_3^-$
(Figure 1) were chosen to validate the OEP\hyp{}based model of the CT energy
at the PT/HF formulation level. Structures of the molecular dimers were first 
energy\hyp{}optimized at the HF/6-31+G(d,p) level by using
the Gaussian 16 quantum chemistry program package.\cite{Gaussian16}
To obtain the PT/HF benchmark CT energy, it was estimated
from the following approximation:
%
\begin{equation}\label{e:ct-pthf-ref}
 \Delta E^{\rm CT}_{\rm PT/HF} \cong \Delta E^{\rm Pol}_{\rm DDS/HF} 
 + \frac{1}{2} {\bf F}^{\rm T} \cdot {\bf D}^{-1} \cdot {\bf F} \;,
\end{equation}
%
where $\Delta E^{\rm Pol}_{\rm DDS/HF}$ is the Hartree\hyp{}Fock polarization energy
defined
according to the density decomposition scheme (here referred as to the DDS) 
proposed by Mandado and Hermida\hyp{}Ram{\'o}n,\cite{Mandado.Hermida-Ramon.JCTC.2011} 
whereas the remainder term is the 
approximate pure induction energy due to the polarizability effects.\cite{Li.Netzloff.Gordon.JCP.2006}
The DDS polarization energy encompasses all the charge delocalization
effects that are not associated with the Pauli exclusion principle
in the first order, and is computed by
%
\begin{multline}\label{e:de-pol-dds}
\Delta E^{\rm Pol}_{\rm DDS/HF} \equiv \Delta E^{\rm HF} \\
 - \left(
   \Delta E^{\rm Coul}_{\rm DDS/HF}
 + \Delta E^{\rm Exch}_{\rm DDS/HF}
 + \Delta E^{\rm Rep}_{\rm DDS/HF} 
   \right)\;.
\end{multline}
%
In the above, $\Delta E^{\rm Coul}_{\rm DDS/HF}$ is the pure Coulombic interaction energy
between the unperturbed (non\hyp{}interacting) charge densities of the monomers in the complex,
and
$\Delta E^{\rm Exch}_{\rm DDS/HF}$ and $\Delta E^{\rm Rep}_{\rm DDS/HF}$
are the exchange and Pauli\hyp{}repulsion interaction energies, respectively. 
At the HF level of theory, their sum is in fact
equivalent to the first\hyp{}order exchange\hyp{}repulsion energy 
in the intermolecular perturbation theory with exchange of Hayes and Stone.\cite{Hayes.Stone.MolPhys.1984} 
It was also shown by 
Mandado and Hermida\hyp{}Ram{\'o}n,\cite{Mandado.Hermida-Ramon.JCTC.2011}
that the Coulombic and exchange\hyp{}repulsion term
in the DDS method reproduce the first\hyp{}order Coulombic and exchange\hyp{}repulsion
interaction energy in the symmetry adapted perturbation theory\cite{Jeziorski.Moszynski.Szalewicz.ChemRev.1994}
(SAPT)
with accuracy below 0.5 kcal/mole.
Therefore, Eq.~\eqref{e:ct-pthf-ref} is believed to be sufficient
in order to compute the PT/HF CT energy, because there is no dispersion
contribution to the DDS polarization energy at the HF level.

The pure induction energy was estimated by using the distributed
dipole\hyp{}dipole polarizability approximation by using the computational
methodology by Li et al.,\cite{Li.Netzloff.Gordon.JCP.2006} 
in which ${\bf F}$ constitutes the electric fields aligned in a super\hyp{}vector 
according to each polarizable center, i.e. ${\bf F} = \{ {\bf F}_1, {\bf F}_2, \ldots\}$,
whereas
the ${\bf D}$ matrix is defined as
%
\begin{equation}
 {\bf D}_{ab} = 
\left\{\begin{matrix}
{\BM\alpha}_a^{-1} &\text{if $a=b$} \\ 
0                  &\text{if $a\ne b \land a,b \in$ same molecule}\\ 
-{\bf T}_{ab}      &\text{if $a\ne b \land a,b \notin$ same molecule}
\end{matrix}\right.
\end{equation}
%
and ${\bf T}_{ab}$ is the dipole\hyp{}dipole interaction tensor
given by
%
\begin{equation}
 {\bf T}_{ab} \equiv \frac{3}{r_{ab}^5} {\bf r}_{ab} \otimes {\bf r}_{ab}
  - \frac{1}{r_{ab}^3} {\bf 1} \;,
\end{equation}
%
with ${\bf r}_{ab} \equiv {\bf r}_{a} - {\bf r}_{b}$ being the
relative distance between the LMO centroids.
The distributed polarizabilities {\bf\textalpha} ${\boldsymbol{\mathrm{\upalpha}}}_a$ centered at the LMO centroids
were computed by utilizing the coupled\hyp{}perturbed Hartree\hyp{}Fock
method.\cite{McWeeny.RevModPhys.1960,Dodds.McWeeney.Sadlej.MolPhys.1977} 
Orbital localization was performed by using the Boys method.\cite{Boys.RevModPhys.1960}

@@

\subsection{\label{s:gsdzdv}Accuracy of OEP-based model}
%
\begin{figure}[t]
\includegraphics[width=0.5\textwidth]{fig-2.eps}
\caption{\label{f:fig-1} {\bf Accuracy of the OEP approach to estimate the charge transfer energy
in the PT/HF formulation.} 
Asymptotic dependencies of the charge transfer energy is plotted for 
(a) water dimer, 
(b) water\hyp{}ammonium complex, and 
(c) ammonium\hyp{}nitrate complex,
where one molecule has been translated by $R$ from the starting geometry
along the vector specified in Fig. 1.
The counterpoise\hyp{}corrected total interaction energy
is also shown for comparison in light grey color in this figure.
All data were obtained at HF/6-31+G** level of theory.
} 
\end{figure}
%

@@

The utmost goal of this work is to reduce the computational cost of
the CT PT/HF energy evaluation in the calculations involving effective fragment
potentials. The EFP2 CT expression has the computational cost
roughly proportional to $(10on^2 + 2n^3 + o^2n^2)v$, where the
$o$ and $n$ denote the number of occupied orbitals and the number of atomic basis functions,
respectively, whereas $v$ is the relative cost. On the other hand, OEP\hyp{}based expression
from Eq.~\eqref{} has the cost of approximately $on(Q+N+o)$, where 
$Q$ and $N$ denote the number of auxiliary basis functions and the number of atoms,
respectively.

In this section, computational cost is estimated from the formulas.
In
Table~\ref{t:oep-costs} 
%
{
\renewcommand{\arraystretch}{1.4}
\begin{table}[b]
\caption[Computational cost of the benchmark and OEP-based methods: calculation of coupling constant]
{{\bf Computational cost of the benchmark and OEP-based methods\footnotemark[1]}
}
\label{t:oep-costs}
\begin{ruledtabular}
\begin{tabular}{lcccccc}
Method             && Murrell et al. &&    EFP2        &&      OEP     \\ 
	\cline{1-7}
Group (i)         &&  &&        &&   $obQ$     \\
Group (ii)        &&  &&        &&   $ob$      \\
Group (iii)       &&  &&        &&   $ob(n+o)$     \\
Total Cost        &&  && $10ob^2 + 2b^3 + o^2b^2$       &&   $ob(Q+n+o)$     \\
\end{tabular}
\end{ruledtabular}
%
\footnotetext[1]{Numbers of: $o$ - occupied molecular orbitals; $b$ - atomic basis functions; $n$ - atoms; 
$Q$ - auxiliary basis functions. It was assumed that the number of virtual orbitals is equal to $b$.}
%
\end{table}
}
%
It is clear that the cost of the OEP\hyp{}based equations is much lesser than the cost of EFP2 method,
and many orders of magnitude lesser than the original theory of Murrell et al.
